Review: The Prevalence of Adaptive Introgression in Crop Histories

### 2018-06-27 paper.tex
edits to conclusions

Additional study of introgression in agroecosystems could lead to advances in crop improvement.
As described above, loci underlying the domesticated phenotype can be more clearly identified by removing the confounding population genetic signals of introgression.
These loci are potentially beneficial targets for crop improvement.
Furthermore, adaptive introgression that is demonstrably tied to a specific environment may include beneficial alleles that can be directly utilized in crop breeding.
Identification of wild relative species or populations that harbor such adaptive genotypes may lead to their prioritization as part of conservation efforts.

@@

As recognized early on by Darwin, crop species represent promising model systems for evolutionary study. 
The application of genomic tools has generated mounting evidence of crop-wild gene flow during and well beyond the initial stages of domestication.
In support of these findings, population genetic theory reinforces the proclivity of native species (in this instance, wild relatives) to provide advantageous, locally adapted alleles to colonizing species (crops) as they disperse beyond their sites of origin into new habitats.
The process of crop range expansion and adaptation through gene flow is closely linked to domestication and, as such, offers new questions and opportunities for practical and theoretical investigation.
As the historic role of wild relatives in the adaptation of crops is clarified, their conservation may be more prioritized, particularly in the face of future climate volatility and change.

Domesticated crops are among humanity's first and greatest inventions.
Interwoven in the genetic history of these crops is the story of our ancestors as they transitioned through the Agronomic Revolution.
In a more nuanced and dynamic understanding of crop domestication that includes sustained gene flow with wild relatives, we gain insight into the evolutionary journey that crops and humanity took, and continue to take, together.

>>>>

Additional study of introgression in agroecosystems could lead to advances in crop improvement.
As described above, loci underlying the domesticated phenotype can be more clearly identified by removing the confounding population genetic signals of introgression.
These loci are potentially beneficial targets for crop improvement and their accurate identification is crucial.
Furthermore, adaptive introgression that is demonstrably tied to a specific environment represents a promising source of beneficial alleles that can be directly utilized in breeding to adapt crops to similar conditions.
Finally, as the historic role of wild relatives in the adaptation of crops is clarified, their conservation may be more prioritized, particularly as a resource for breeding in the face of future climate volatility and change.

@@

As recognized early on by Darwin, crop species represent promising model systems for evolutionary study. 
The application of genomic tools has generated mounting evidence of crop-wild gene flow during and well beyond the initial stages of domestication.
The process of crop range expansion and adaptation through gene flow is closely linked to domestication and offers new questions and opportunities for practical and theoretical investigation.
Domesticated crops are among humanity's first and greatest inventions.
Interwoven in the genetic history of these crops is the story of our ancestors as they transitioned through the Agronomic Revolution.
In a more nuanced and dynamic understanding of crop domestication that includes sustained gene flow with wild relatives, we gain insight into the evolutionary journey that crops and humanity took, and continue to take, together.
